Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-09 Presentation/gpm_november2016_vianello.tex
Update to the presentation
Included MAST L-Mode, AUG H-Mode and open issues

  \begin{frame}{L-Mode: JET}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> The shoulder formation strongly depends on
        divertor geometry, disappear with vertical target and strike
        point closest to cryogenics pumps \parencite{Wynn:EPS2016}
      \item<2|only@2> The midplane pressure from baratrons is
        equivalent between the different divertor. \alert{This would
          indicate that SOL neutral density does not play any role}
       \item<3|only@3> In the horizontal target configuration the
         results indicate that the shoulder forms right at the
         transition from sheath-limited to high-recycling where also
         $\Lambda_{div}$ strongly increase
       \item<4|only@4> Shoulder amplitude correlates with strike
         points position. \alert{Shoulder, ionization and
           $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
         from the pump}
       \item<5|only@5> In seeded discharges the transition observed at
         very high level of $\Lambda_{div} >> 1$
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16b}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16c}
        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16d}
        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16e}
      \end{column}
    \end{columns}

>>>>

  \begin{frame}{L-Mode: JET}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> The shoulder formation strongly depends on
        divertor geometry, disappear with vertical target and strike
        point closest to cryogenics pumps \parencite{Wynn:EPS2016}
      \item<2|only@2> The midplane pressure from baratrons is
        equivalent between the different divertor. \alert{This would
          indicate that SOL neutral density does not play any role}
       \item<3|only@3> In the horizontal target configuration the
         results indicate that the shoulder forms right at the
         transition from sheath-limited to high-recycling where also
         $\Lambda_{div}$ strongly increase
       \item<4|only@4> Shoulder amplitude correlates with strike
         points position. \alert{Shoulder, ionization and
           $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
         from the pump}
       \item<5|only@5> In seeded discharges the transition observed at
         very high level of $\Lambda_{div} >> 1$
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16b}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16c}
        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16d}
        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16e}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: MAST}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> Strong dependence on
        I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
        constant toroidal field shoulder disapper. Consistent with
        observation in other devices
      \item<2|only@2> Filaments binormal dimension increases with
        current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
       \item<3|only@3> Filament radial velocity decreases with current
         as well as the radial dimension \parencite{Kirk:2016jj}
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MilitelloNF16a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16a}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16c}
      \end{column}
    \end{columns}
  \end{frame}

  \section{H-Mode}
  \begin{frame}{AUG: H-Mode}
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item<1|only@1> SOL profiles in H-Mode so far investigated on
        AUG \parencite{Muller:2015jt,Sun:2015bu}
      \item<2|only@2> Differently from L-Mode, complete detachment
        suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
       \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
         shoulder depends on a combination of $\Lambda_{div}$ and
         fueling rate
      \end{itemize}
    \end{column}
      \begin{column}{0.6\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MuellerJNM15a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/SunPPCF15a}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16i}
      \end{column}
    \end{columns}
  \end{frame}

  \section{Open issue}
  \begin{frame}{Open and unresolved issues}
  \setbeamercovered{transparent}
  \begin{enumerate}[<+(1) | invisible@-+>]
    \item Does $\Lambda_{div}$ unifies the picture among the devices?
      \alert{No, a dependence on neutral pressure is likely to play a role}
    \item If neutrals play a role is the divertor or midplane?
      \alert{Contradictory results if one include experiments with
        midplane puffing, JET and EIRENE simulations}
    \item Does L$_\parallel$ plays any role? \alert{So far TCV suggests no
      dependence from f$_x$ scan but both TCV and MAST observe an
      I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
      increases with L$_{\parallel}$ }
    \item Cooling the divertor with fueling or seeding is really
      equivalent? \alert{Contradictory observation in AUG and JET}
    \item Can be translate straightforward from L to H-Mode? \alert{So
      far no as shown in H-Mode AUG. We need higher detachment
      condition and we need enough fueling}
    \end{enumerate}
